Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-27 Paper/MSRChallenge2017.tex
acks
shorter roadmap

We created decision tree classifiers~\cite{Quinlan86} to address our main research question: ``Do social attributes, gathered 
from the GitHub profiles of developers,
allow for more accurate predictions than only using technical data?''
%   The predicted class is represented as the
% leaves, while the attribute decisions used in the prediction cause the
% different branches.
We used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
with default settings. We mitigate the risk of overfitting through 10-fold 
cross-validation.

In Section~\ref{sec:successClassification} we discuss the build classification
success rate for the technical and social factors.  In Section~\ref{sec:core},
we compare the build success rate of core project members to non-core project
members.  In Section~\ref{sec:followerSuccess}, we compare the relationship
between a developer's followers and build integration success. We conclude the
section with a discussion of threats to validity (Section~\ref{sec-threats}).

@@

\subsection{Threats to validity}
\label{sec-threats}

@@

% use section* for acknowledgement
\section*{Acknowledgment}

The acknowledgments will be added for the camera ready version.

>>>>

We assess our main research question using decision tree
classifiers~\cite{Quinlan86}, using
%
% to address our main research question: ``Do social attributes, gathered 
%from the GitHub profiles of developers,
%allow for more accurate predictions than only using technical data?''
%   The predicted class is represented as the
% leaves, while the attribute decisions used in the prediction cause the
% different branches.
the Weka J48 decision tree~\cite{Weka,Quinlan1993}
with default settings and 10-fold 
cross-validation.
We present classification
success rate for technical versus social factors
(Section~\ref{sec:successClassification}); 
build success rate of core project members versus non-core 
members (Section~\ref{sec:core}); and the relationship 
between follower count and build success (Section~\ref{sec:followerSuccess}).

@@

\section{Threats to validity}
\label{sec-threats}

@@

% use section* for acknowledgement
\section*{Acknowledgments}

The authors gratefully acknowledge the partial support
of the AFRL under AFRL Contract No. FA8750-15-2-0075. Any views, opinions,
findings or recommendations are those of the author(s) and do not
necessarily reflect the views of the sponsoring agencies.
